Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
food and stuff
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

We implement the sequencer service in Malacology as an application-specific
file type that attaches a 64-bit value to the inode state within the Ceph
metadata service.

The zlog sequencer is volatile, shared resource that requires serialized
access. in corfu the sequencer is a fast, centeralized network counter
resource.

Initially we saught to directly model the sequencer in ceph as a non-exclusive,
non-cacheable resource, forcing clients to perform round-trip access the
resource at the authoratiave MDS for the inode representing the sequencer.
However, we found that the capapbility system in Ceph is used to batch access
to cacheable resources, providing clients best-effort access to the capability
and allowing them to burst. While unexpected, this alternative mode provides
a different approach to sequencer implementation.

In Section we quantify the trade-offs of throughput and latency for the
centeralized sequencer and the batching mechanism based on capabilities.

The MDS has a queue of locks that it uses to revoke capabilities from
the clients. If we put a Mantle-style hook here, we can control when
those revoke messages go out.

Mantle is used to implement a zlog file type specific policy for maximizing
throughput to the sequencer by migration the resource between metadata servers.

Sequencer recovery is handled by tapping into existing recovery mechanisms
that recover inode state. file type specific recovery augments the existing
recovery procedure.

\subsubsection{Log Management}

log management is supported by mds using a special directory layout
and file types.

\subsubsection{Storage Interface Management}

lua snippet

The lua implementation of the interfaces are encoded into cluster maps
for automatic verisoning and dissemtation across the cluster.

>>>>

We implement the sequencer service in Malacology as an application-specific
file type that associates a small amount of metadata, including the 64-bit log
tail position, to the inode state managed by the Ceph metadata service.  Since
a sequencer is associated with a unique log, this approach has the added
benefit of allowing the metadata service to also handle naming, by
representing each log service instance within the standard POSIX hierarchical
namespace.

{\bf Physical design.}
The next component of our design is the low-level configuration of the
sequencer inode type that achieves the correct semantics.  Initially we sought
to directly model the sequencer service in Ceph as a non-exclusive,
non-cacheable resource, forcing clients to perform a round-trip access to the
resource at the authoratiave metadata server for the inode representing the
sequencer.  Interestingly, we found that the capapbility system in Ceph uses a
strategy to reduce metadata service load by allowing multiple clients that
open a shared file to temporarily cache the inode resource, resulting in a
round-robin, best-effort batching behavior. When a single client is accessing
the sequencer resource it is able to cache state locally without interruption.

While unexpected, this discovery allowed us to explore an implementation
strategy that we had not previously considered. In particular, for bursty
clients and clients that can tolerate high latency, this mode of operation may
allow a system to achieve much higher throughput than a system with a
centralized sequencer service.

In Section we quantify the trade-offs of throughput and latency for an
approach based on a round-robin batching mode, and compare this mode to one in
which the metadata server mediates access to the sequencer state when in it is
being shared among multiple clients.

{\bf Capability policies.}
We use capabilitity policies in the metadata service to tune the amount of
time that clients may cache the sequencer resource. This allows us to control
the trade-off between latency and throughput beyond the standard best-effort
policy.

{\bf Balancing policies.}
While the metadata service is a shared resource, authority over metadata
resources can be physically moved between servers using a dynamic, ZLog-aware
policy expressed in Mantle. For instance, one or more metadata servers may be
dedicated to supporting ZLog sequencer load. When the system load is low all
resources are spread evenly, but non-ZLog resources may be migrated to
best-effort servers when sequencer performance suffers.

{\bf Recovery.}
What?
